 %\documentclass[aps,prb,twocolumn,showpacs,groupedaddress]{revtex4}
\documentclass[aps,prb,twocolumn,showpacs,groupedaddress]{revtex4-1}

%\usepackage[printfigures]{figcaps}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{float}
%\usepackage{caption}
\usepackage{subfigure}
%\usepackage{tikz}

%\newcommand{\bs}[1] {\boldsymbol{#1}}
\newcommand{\bs}[1] {\mathbf{#1}}
\newcommand{\ve}{V}
\newcommand{\fl} [2]{#1^{\Lambda}_{\mathrm{#2} }  }

%\setlength{\parskip}{\plus4mm minus3mm}
%\makeatletter% Set distance from top of page to first float
%\setlength{\@fptop}{-10pt}
%\makeatother

\begin{document}

%\title{Frequency dependent functional renormalization group flow}
\title{Non-separable frequency dependence of two-particle vertex \\ 
        in interacting fermion systems}

\author {D.~Vilardi}
\author{C.~Taranto}
\author{W.~Metzner}
\affiliation{Max Planck Institute for Solid State Research, Heisenbergstrasse 1, D-70569 Stuttgar, Germany}

\date{\today}

\begin{abstract}
We derive functional flow equations for the two-particle vertex and the self-energy in interacting fermion systems which capture the full frequency dependence of both quantities. The equations are applied to the hole-doped two-dimensional Hubbard model as a prototype system with entangled magnetic, charge and pairing fluctuations. Each fluctuation channel acquires substantial dependences on all three Matsubara frequencies, such that the frequency dependence of the vertex cannot be accurately represented by a channel sum with only one frequency variable in each term. At the temperatures we are able to access, the leading instabilities are mostly antiferromagnetic, with an incommensurate wave vector. However, at large doping, a divergence in the charge channel occurs at a finite frequency transfer, if the vertex flow is computed without self-energy feedback. This enigmatic instability was already observed in a calculation by Husemann \emph{et al.} [Phis.~Rev.~B, \textbf{85}, 075121 (2012)], who used an approximate separable ansatz for the frequency dependence of the vertex. We identify a simple mechanism for this instability in terms of a random phase approximation for the charge channel with a frequency dependent effective magnetic interaction as input.
The frequency dependent self-energy is generically affected only mildly by the strongly momentum and frequency dependent two-particle vertex. At the moderate interaction strength where our approach is applicable, we obtain a moderate reduction of the quasi-particle weight and a sizable decay rate with a pronounced momentum dependence. Nevertheless, the self-energy feedback into the vertex flow turns out to be crucial, as it suppresses the unphysical finite frequency charge instability.
\end{abstract}

\pacs{}
\maketitle

\section{Introduction}
\label{sec:introduction}
\input{content/Introduction.tex}

\section{Formalism}
\label{sec:formalism}
\input{content/fRG.tex}
\section{Vertex approximation}
\label{sec:vertex}
\input{content/VertexApproximation.tex}

\section{Results}
\label{sec:results}
\input{content/Results.tex}

\section{Conclusions}
\label{sec:conclusions}
\input{content/Conclusions.tex}

\vspace*{5mm}
\begin{acknowledgments} 
We are grateful to M.~Salmhofer, A.~Eberlein, S.~Andergassen, A.~Toschi for useful discussion. 
We thank O.~Gunnarsson for a critical reading of the manuscript and D.~T.~Mantadakis for comments and suggestions. 
\end{acknowledgments}

\begin{appendix}
\input{content/Appendices.tex}
\end{appendix}

\bibliography{refs}
%\bibliographystyle{unsrt}
\bibliographystyle{apsrev4-1}


\end{document}
