\subsection{Frequency dependence of Vertex}

\begin{itemize}

\item Forward scattering problem seen by Salmhofer

\item Show phase diagram, $\Lambda_{cri}$ vs $x=1-n$, with and without $\Sigma$ 
          (for differenct $t'$)
          
\item Self energy "solve" the problem of charge instability.

\item Suggestion: The charge problem exists also at van Hove filling where, according to the literature, 
           the $\Sigma$ has no effect when Karrasch approximation is taken into account.

\item  Colorplots: Mag and Charge channel

\end{itemize}

While much of the weak coupling momentum structure of the vertex (for the fermionic Hubbard model) is know by means of fRG, its frequency structure has been investigated much less. 
In recent years several results have been obtained for the single impurity Anderson model vertex, both on its own and as essential ingredient for diagrammatic extensions of DMFT. 
Citare: Rohringer, Kinza, Hafermann, Karrasch, Wentzell (and references therein) for the SIAM. Extensions of DMFT: DGA, DF, DMF2RG, Trilex, Quadrilex. 
However a systematic study keeping into account the full frequency dependence and a physically motivated approximation for the momentum dependence, and including fluctuations in all channels is still lacking.

In this persepctive we will present, in the next section, our results obtained by means of fully frequency dependent fRG.
From the methodologic point of view, these results have to be considered as a proof of principle of the feasibility, and in some resepcts of the necessity, of a complete treatment of the frequency dependence of the vertex, with an impact on methods that aim at the study of strong coupling.
From a more physical persepctive we will confirm some results already foreseen by \onlinecite{Husemann2012} with a simpler frequency parametrization. However the study of the frequncy dependence of the verttex will allow us to gain a deeper understanding in these results, in particular the appearance of a \textit{scattering instability}, and a sensitive reduction of the $d$-wave channel. 

Furthermore, a frequency dependent vertex also allows us to compute the frequency dependent self energy, a task that, within fRG, requires heavier approximations whenver one restricts himself to a static vertex.  
We will show that the self-energy feedback in the flow equations is essential to guarantee the consistency between vertex and propagators in the flow equations.
In fact, it turns out that even a Fermi-liquid self-energy can qualitatively change the physical results. 

\paragraph*{Numerical implementation}
We have implemented numerically the flow equations reported in the appendix. 

Due to the different nature of the momentum arguments of self-energy and vertex we have defined two different patching of the irreducible Brillouin zone. 
%The $\phi$-functions depend on a momentum transfer.  
%For the filling and nearest neighbors hopping that we want to describe, the momentum vectors of the most relevant process are $\mathbf{Q}=(0,0)$, important for superconductivity (in the pairing channel) and ferromagnetism (in the magnetic channel); $\mathbf{Q}=(\pi,\pi)$ and its vicinity, relevant for antiferromagnetism and incommensurate antiferromagnetism; the momentum transfer $2k_F$, as defined in Ref.~\onlinecite{Holder2014}, associated to the onset of charge- and spin-density wave instabilities. 
Similarly to what is done in Ref.~\onlinecite{Husemann2009}, the vertex patching describes more accurately the corners around $(0,0)$ and $(\pi,\pi)$, where, for the cases that we will consider, the instability vectors are located.

The situation is completely different for the self-energy, for which the most relevant physics happens in the vicinity of the Fermi surface, at least in the weak coupling regime. Therefore we chose to concentrate the patches along the Fermi surface and in its immediate vicinity, with some further care close to the antinodal points near $(\pi,0)$, relevant for the physics of antiferromagnetism and pseudogap. The representative points are visualized in Fig. (occupation). 

%It is not necessary  that the patching-schemes for vertex and self-energy are connected, but the number of patches used should be roughly of the same order.
In the calculations presented in the following we have used $29$ patches for the vertex and $44$ for the self-energy.

For the practical implementation of the frequency dependence we found convenient to rewrite $\mathcal{S}$, $\mathcal{D}$, $\mathcal{C}$ and $\mathcal{M}$ as function of three bosonic frequencies. 
For each frequency argument we restricted ourselves to at least $40$ positive and $40$ negative Matsubara frequencies. 
We stress that the number of Matsubara frequencies that can be taken into account in the calculation sets the lowest reachable temperature.
  


\subsection{Forward scattering problem}

\begin{itemize}

\item Introduce perpendicular ladder (PL) for charge.

\item Colorplot of charge in PL.

\item Discuss the role of the Bubble at $\boldsymbol{Q}=(0,0)$ and plot it as a function of $\nu$.

\end{itemize}

\subsection{Self energy effects}

\begin{itemize}

\item With self energy feedback, we didn't find any charge instability problem for any parameters range studied.

\item Plot of the Fermi surface based patch scheme.

\item Plot of $\Sigma(i\omega)$ at $\boldsymbol{k}=(\pi,0)$, $\boldsymbol{k}=\boldsymbol{k}_{HS}$ and $\boldsymbol{k}=(\pi/2,\pi/2)$ in frequency space.

\item Plot of $Z_{\boldsymbol{k}}$

\item Plot of occupation with and without $\Sigma$

\end{itemize}